{\includegraphics[width=3cm, height=2.5cm]{Cran.jpg}} \\ \includegraphics[width=7cm, height=1cm]{TB.jpg} \\ {Technical Documentation for TersectBrowser+}

### 2025-05-05 TechDoc/TechDoc.tex
Adding in diagrams

\paragraph{Feature Description}
\begin{itemize}
    \item JBrowse window:
    \begin{itemize}
        \item Main window is located at the top of Tersect Browser, below settings bar but above the heatmap 
        \item Main window shows only sequence tracks and linear genome scale. Interactive features such as zoom anc chromosome selection have been removed from the main window. The container window has a dynamic offset, which changes according to tree view and zoom level to ensure the chromosome scales between TersectBrowser and JBrowse line up. 
        \item By default, the main window shows only the gene models track.
        \item Popup window provides a more sandbox experience, providing more user interaction. The user can change zoom level and displayed chromosome, and two scale bars enable both precise and rapid navigation. The hamburger menu on the top left provides the capability for the user to upload their own data to visualise unique tracks.
        \item By default, the popup window shows the reference sequence track, gene models track, and variant track for the specified accession.
    \item Tracks:
    \begin{itemize}
        \item Reference sequence 
        \item Variant tracks for each loaded accession
        \item Gene models FeatureTrack (\nameref{sec:Models})
    \end{itemize}
    \item Syncing of the JBrowse window and the TersectBrowser heatmap includes the following:
    \begin{itemize}
        \item Zoom - both by clicking the plus/minus buttons and by scrolling with the mouse wheel.
        \item Bin size.
        \item Selected interval.
        \item Chromosome.
        \item Horizontal scrolling along the x-axis.
    \end{itemize}
\end{itemize}

@@

\paragraph{Feature Description}
\begin{itemize}
    \item \verb+Open Variant Search+ button in TersectBrowser+ header, opens popup window for user to select advanced features.
    \item Popup window where user can select interval, choose impact level, and search button to initiate search.
    \item Output: Bins in the canvas are highlighted red at the chromosomal position where the variant is located, and only for accessions containing variants of the specified impact.
    \item Clear button located in TersectBrowser+ header to clear highlighted bins from canvas and restore original heatmmap.
\end{itemize}
\paragraph{\hl{Search Bar}}
\paragraph{\hl{Popup window with advanced settings }}
\paragraph{Highlighting bins}
Bin highlighting is controlled in the \verb+bin-draw.service+ by two functions. The first function, \verb+highlightFeatureBins()+, is defined, taking as arguments a string containing accession names, the bin position along the x-axis, and the \verb+binView+. First, the y-axis bin position for accession names is calculated. Then, the \verb+binView+ is redrawn in greyscale, with the bin colour determined by the difference to the reference accession. Using the x-axis \verb+binIndex+ position and the y-axis accession bin positions, these bins are coloured red in the \verb+binView+. The modified \verb+binView+ is returned as the output. The second function, \verb+highlightBins()+, takes as arguments the start position of the interval and the bin size currently shown in the Tersect pane, a list of ordered accessions shown in the canvas, and the searched accessions. For each searched accession, accession name is reformatted to match the format displayed in the Tersect pane. Then, the bin position along the x-axis is calculated using the \verb+getBinIndexFromPosition()+ function, which takes as arguments the feature position along the chromosome, the interval start position, and the bin size. Then, \verb+highlightFeatureBins()+ is called for each accession. Lastly, the canvas is redrawn using the modified \verb+binView+ output from \verb+highlightFeatureBins()+. 
\begin{itemize}
    \item highlightFeatureBins(accessions: string[], binIndex: number, binView: DistanceBinView) - takes a string of accession names, a binIndex (corresponding to the bin position along the x-axis matching the gene position on the chromosome), and binView. The y-axis index for bins matching accession names in the accessions strings is calculated and combined with the binIndex to colour these specific bins red. The rest of the bins are coloured in greyscale, with saturation depending on binDistance (calculated from tersect on the backend 
    \begin{itemize}
        \item Bin-draw.service.ts 
        \item Called by highlightBins() in bin-draw.service.ts 
    \end{itemize}
    \item highlightBins(intervalStart, binsize, orderedAccessions, searchedAccessions) - takes selected interval start position, selected binSize, list of ordered accessions shown in the canvas, and searched accessions (passed from callback function?). Accession names in Jbrowse are in a different format to what is stored in tersect browser, so accession names are reformatted to match tersect browser bins. binIndex is calculated for the selected gene. These two are passed to highlightFeatureBins() - along with this.bins - to highlight the bins. The canvas is then redrawn using the binView calculated in highlightFeatureBins(). 
    \begin{itemize}
        \item Bin-draw.service.ts 
        \item Called by callHighlightBins() in tersect-browser.component.ts 
    \end{itemize}
    \item callHighlightBins(searchedAcessions) - takes searchedAccessions. Calls highlightBins(), passing along  selected interval start position, selected binSize, list of ordered accessions shown in the canvas, and searched accessions (passed from callback function?). 
    \begin{itemize}
        \item Tersect-browser.component.ts 
    \end{itemize}
\end{itemize}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=5cm, height=9cm]{UserBarcode.jpg}
    \caption{User-focused data flow through Barcoding Extension.}
\end{figure}
\paragraph{Frontend Display Feature Description}
When the user clicks on a bin, the popup menu appears and the button "Create barcode" is visible, styled with a barcode icon. When the user clicks on this button, a popup window appears in the centre of the screen. The window title is the corresponding accession name. The window contains the header "Barcode Generator" and contains a description of what is being generated. There is a box for the user to input barcode size, with default set to 150, and the maximum number of variants allowed per barcode (this is an optional parameter. Leaving this blank means all possible barcodes will be returned).

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=7cm, height=12cm]{ExtBarcode.jpg}
    \caption{User-focused data flow through Barcoding Extension.}
\end{figure}

>>>>

\subsubsection{User Interface}
\begin{figure}[h]
    \centering
    \includegraphics[width=10cm, height=8cm]{GenomeBrowser.png}
    \caption{UI diagram for Genome Browser.}
\end{figure}

\paragraph{Feature Description}
\begin{itemize}
    \item JBrowse window:
    \begin{itemize}
        \item Main window is located at the top of Tersect Browser, below settings bar but above the heatmap 
        \item Main window shows only sequence tracks and linear genome scale. Interactive features such as zoom anc chromosome selection have been removed from the main window. The container window has a dynamic offset, which changes according to tree view and zoom level to ensure the chromosome scales between TersectBrowser and JBrowse line up. 
        \item By default, the main window shows only the gene models track.
        \item Popup window provides a more sandbox experience, providing more user interaction. The user can change zoom level and displayed chromosome, and two scale bars enable both precise and rapid navigation. The hamburger menu on the top left provides the capability for the user to upload their own data to visualise unique tracks.
        \item By default, the popup window shows the reference sequence track, gene models track, and variant track for the specified accession.
    \item Tracks:
    \begin{itemize}
        \item Reference sequence 
        \item Variant tracks for each loaded accession
        \item Gene models FeatureTrack (\nameref{sec:Models})
    \end{itemize}
    \item Syncing of the JBrowse window and the TersectBrowser heatmap includes the following:
    \begin{itemize}
        \item Zoom - both by clicking the plus/minus buttons and by scrolling with the mouse wheel.
        \item Bin size.
        \item Selected interval.
        \item Chromosome.
        \item Horizontal scrolling along the x-axis.
    \end{itemize}
\end{itemize}
\end{itemize}

@@

\subsubsection{User Interface}
\begin{figure}[h]
    \centering
    \includegraphics[width=15cm, height=9cm]{FS1.png}
    \caption{UI digram for Feature Search.}
\end{figure}

\paragraph{Feature Description}
\begin{itemize}
    \item \verb+Open Variant Search+ button in TersectBrowser+ header, opens popup window for user to select advanced features.
    \item Popup window where user can select interval, choose impact level, and search button to initiate search.
    \item Output: Bins in the canvas are highlighted red at the chromosomal position where the variant is located, and only for accessions containing variants of the specified impact.
    \item Clear button located in TersectBrowser+ header to clear highlighted bins from canvas and restore original heatmmap.
\end{itemize}
\subsubsection{Technical Description}

\begin{figure}[h]
    \centering
    \includegraphics[width=7cm, height=15cm]{FS2.png}
    \caption{Data flow diagram for Feature Search.}
\end{figure}

\paragraph{\hl{Search Bar}}
\paragraph{\hl{Popup window with advanced settings }}
\paragraph{Highlighting bins}
Bin highlighting is controlled in the \verb+bin-draw.service+ by two functions. The first function, \verb+highlightFeatureBins()+, is defined, taking as arguments a string containing accession names, the bin position along the x-axis, and the \verb+binView+. First, the y-axis bin position for accession names is calculated. Then, the \verb+binView+ is redrawn in greyscale, with the bin colour determined by the difference to the reference accession. Using the x-axis \verb+binIndex+ position and the y-axis accession bin positions, these bins are coloured red in the \verb+binView+. The modified \verb+binView+ is returned as the output. The second function, \verb+highlightBins()+, takes as arguments the start position of the interval and the bin size currently shown in the Tersect pane, a list of ordered accessions shown in the canvas, and the searched accessions. For each searched accession, accession name is reformatted to match the format displayed in the Tersect pane. Then, the bin position along the x-axis is calculated using the \verb+getBinIndexFromPosition()+ function, which takes as arguments the feature position along the chromosome, the interval start position, and the bin size. Then, \verb+highlightFeatureBins()+ is called for each accession. Lastly, the canvas is redrawn using the modified \verb+binView+ output from \verb+highlightFeatureBins()+. 
\begin{itemize}
    \item highlightFeatureBins(accessions: string[], binIndex: number, binView: DistanceBinView) - takes a string of accession names, a binIndex (corresponding to the bin position along the x-axis matching the gene position on the chromosome), and binView. The y-axis index for bins matching accession names in the accessions strings is calculated and combined with the binIndex to colour these specific bins red. The rest of the bins are coloured in greyscale, with saturation depending on binDistance (calculated from tersect on the backend 
    \begin{itemize}
        \item Bin-draw.service.ts 
        \item Called by highlightBins() in bin-draw.service.ts 
    \end{itemize}
    \item highlightBins(intervalStart, binsize, orderedAccessions, searchedAccessions) - takes selected interval start position, selected binSize, list of ordered accessions shown in the canvas, and searched accessions (passed from callback function?). Accession names in Jbrowse are in a different format to what is stored in tersect browser, so accession names are reformatted to match tersect browser bins. binIndex is calculated for the selected gene. These two are passed to highlightFeatureBins() - along with this.bins - to highlight the bins. The canvas is then redrawn using the binView calculated in highlightFeatureBins(). 
    \begin{itemize}
        \item Bin-draw.service.ts 
        \item Called by callHighlightBins() in tersect-browser.component.ts 
    \end{itemize}
    \item callHighlightBins(searchedAcessions) - takes searchedAccessions. Calls highlightBins(), passing along  selected interval start position, selected binSize, list of ordered accessions shown in the canvas, and searched accessions (passed from callback function?). 
    \begin{itemize}
        \item Tersect-browser.component.ts 
    \end{itemize}
\end{itemize}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=6cm, height=8cm]{Bar1.png}
    \caption{UI diagram for Barcode Generation.}
\end{figure}

\paragraph{Frontend Display Feature Description}
When the user clicks on a bin, the popup menu appears and the button "Create barcode" is visible, styled with a barcode icon. When the user clicks on this button, a popup window appears in the centre of the screen. The window title is the corresponding accession name. The window contains the header "Barcode Generator" and contains a description of what is being generated. There is a box for the user to input barcode size, with default set to 150, and the maximum number of variants allowed per barcode (this is an optional parameter. Leaving this blank means all possible barcodes will be returned).

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=7cm, height=15cm]{Bar2.png}
    \caption{Data flow diagram for Barcode Generation.}
\end{figure}
